Navigating to a greener Europe with 24/7 hourly carbon-free electricity procurement

### 2023-10-10 manuscript/manuscript.tex
references: solve URL brake issue with xurl
intro: outline section
intro: complete section
manuscript: coordinate all chapters, complete methods

% format hacks
\usepackage{libertine}
\usepackage{libertinust1math}
\usepackage{amsmath}                 % Provides advanced math typesetting and environments
\usepackage{bbold}                   % Provides blackboard bold font for numbers
\usepackage{graphicx}                % Handles the inclusion of graphics files
\usepackage{eurosym}                 % Provides the Euro currency symbol
\usepackage{mathtools}               % Enhances amsmath package, adding new symbols and tools
\usepackage{url}                     % Handles the formatting of URLs
\usepackage{booktabs}                % Improves the quality of tables in LaTeX
\usepackage{epstopdf}                % Automatically converts EPS files to PDF
\usepackage{xfrac}                   % Provides a consistent way to typeset fractions
\usepackage{tabularx}                % Enhances the standard LaTeX tables
\usepackage{bm}                      % Provides access to bold math symbols
\usepackage{subcaption}              % Provides support for subfigures and subtables
\usepackage{longtable}               % Allows the creation of multi-page tables
\usepackage{multirow}                % Enables cells spanning multiple rows in tables
\usepackage{threeparttable}          % Provides additional functionality for tables
\usepackage{pdflscape}               % Allows landscape pages in PDF output
\usepackage[svgnames]{xcolor}    	 % Load xcolor packages
\usepackage[export]{adjustbox}       % Provides tools for resizing and trimming images
\usepackage[version=4]{mhchem}       % Provides typesetting for chemical equations
\usepackage[colorlinks]{hyperref}    % Creates hyperlinks in the document
\usepackage[parfill]{parskip}        % Adjusts paragraph spacing
\usepackage[nameinlink,sort&compress,capitalise,noabbrev]{cleveref} % Enhanced cross-referencing
\usepackage[leftcaption,raggedright]{sidecap} % Provides side captions for figures and tables
\usepackage[prependcaption,textsize=footnotesize]{todonotes} % Allows inline and margin notes
\usepackage{siunitx}                 % Provides consistent formatting for units and numbers
\usepackage[acronym, automake, nonumberlist]{glossaries-extra}

@@

% Proper nouns
\newacronym{EU}{EU}{European Union}
\newacronym{bdew}{BDEW}{Bundesverband der Energie- und Wasserwirtschaft}
\newacronym{dea}{DEA}{Danish Energy Agency}
\newacronym{jrc}{JRC}{Joint Research Center}
\newacronym{tyndp}{TYNDP}{Ten-Year Network Development Plan}
\newacronym{entsoe}{ENTSO-E}{European Network for Transmission System Operators for Electricity}
\newacronym{entsog}{ENTSO-G}{European Network of Transmission System Operators for Gas}

@@

% Energy economics and finance concepts
\newacronym{fom}{FOM}{Fixed Operation and Maintenance costs}
\newacronym{vom}{VOM}{Variable Operation and Maintenance costs}
\newacronym{capex}{CAPEX}{Capital expenditures}
\newacronym{opex}{OPEX}{Operational expenditures}
\newacronym{ppa}{PPA}{Power Purchase Agreement}
\newacronym{ptc}{PTC}{Production Tax Credit}
\newacronym{necp}{NECP}{National Energy and Climate Plan}
\newacronym{ets}{ETS}{Emissions Trading System}
\newacronym{cfd}{CfD}{Contract for Difference}

% Other
\newacronym{pypsa}{PyPSA}{Python for Power System Analysis}
\newacronym{nuts}{NUTS}{Nomenclature of Territorial Units for Statistics}
\newacronym{ci}{C\&I}{Corporate and Industry (sectors)}

@@

	\title{Navigating to a greener Europe with 24/7 hourly clean electricity procurement}

@@

\section{Methods}
\label{sec:methods}
\input{sections/methods.tex}

@@

@@

\section{Supplementary Information}
\label{sec:si}

\input{sections/supplementary.tex}

\addcontentsline{toc}{section}{Supplementary References}
\renewcommand{\ttdefault}{\sfdefault}
\bibliographyS{references}

>>>>

% format hacks
\usepackage{libertine}
\usepackage{libertinust1math}
\usepackage{amsmath}                 % Provides advanced math typesetting and environments
\usepackage{bbold}                   % Provides blackboard bold font for numbers
\usepackage{graphicx}                % Handles the inclusion of graphics files
\usepackage{eurosym}                 % Provides the Euro currency symbol
\usepackage{mathtools}               % Enhances amsmath package, adding new symbols and tools
\usepackage{url}                     % Handles the formatting of URLs
\usepackage{booktabs}                % Improves the quality of tables in LaTeX
\usepackage{epstopdf}                % Automatically converts EPS files to PDF
\usepackage{xfrac}                   % Provides a consistent way to typeset fractions
\usepackage{tabularx}                % Enhances the standard LaTeX tables
\usepackage{bm}                      % Provides access to bold math symbols
\usepackage{subcaption}              % Provides support for subfigures and subtables
\usepackage{longtable}               % Allows the creation of multi-page tables
\usepackage{multirow}                % Enables cells spanning multiple rows in tables
\usepackage{threeparttable}          % Provides additional functionality for tables
\usepackage{pdflscape}               % Allows landscape pages in PDF output
\usepackage[svgnames]{xcolor}    	 % Load xcolor packages
\usepackage[export]{adjustbox}       % Provides tools for resizing and trimming images
\usepackage[version=4]{mhchem}       % Provides typesetting for chemical equations
\usepackage{xurl} 				     % Allows line breaks in URLs
\usepackage[colorlinks]{hyperref}    % Creates hyperlinks in the document
\usepackage[parfill]{parskip}        % Adjusts paragraph spacing
\usepackage[nameinlink,sort&compress,capitalise,noabbrev]{cleveref} % Enhanced cross-referencing
\usepackage[leftcaption,raggedright]{sidecap} % Provides side captions for figures and tables
\usepackage[prependcaption,textsize=footnotesize]{todonotes} % Allows inline and margin notes
\usepackage{siunitx}                 % Provides consistent formatting for units and numbers
\usepackage{csquotes} 				 % For handling inline and display quotations
\usepackage[acronym, automake, nonumberlist]{glossaries-extra}

@@

% Proper nouns
\newacronym{eu}{EU}{European Union}
\newacronym{bdew}{BDEW}{Bundesverband der Energie- und Wasserwirtschaft}
\newacronym{dea}{DEA}{Danish Energy Agency}
\newacronym{jrc}{JRC}{Joint Research Center}
\newacronym{tyndp}{TYNDP}{Ten-Year Network Development Plan}
\newacronym{entsoe}{ENTSO-E}{European Network for Transmission System Operators for Electricity}
\newacronym{entsog}{ENTSO-G}{European Network of Transmission System Operators for Gas}

@@

% Energy economics and finance concepts
\newacronym{fom}{FOM}{Fixed Operation and Maintenance costs}
\newacronym{vom}{VOM}{Variable Operation and Maintenance costs}
\newacronym{capex}{CAPEX}{Capital expenditures}
\newacronym{opex}{OPEX}{Operational expenditures}
\newacronym{ppa}{PPA}{Power Purchase Agreement}
\newacronym{ptc}{PTC}{Production Tax Credit}
\newacronym{necp}{NECP}{National Energy and Climate Plan}
\newacronym{ets}{ETS}{Emissions Trading System}
\newacronym{cfd}{CfD}{Contract for Difference}
\newacronym{go}{GO}{Guarantees of Origin}
\newacronym{rec}{REC}{Renewable Energy Certificate}

% Other
\newacronym{pypsa}{PyPSA}{Python for Power System Analysis}
\newacronym{nuts}{NUTS}{Nomenclature of Territorial Units for Statistics}
\newacronym{ci}{C\&I}{Corporate and Industry (sectors)}
\newacronym{ngo}{NGO}{Non-Governmental Organization}

@@

	\title{Navigating to a greener Europe with 24/7 hourly carbon-free electricity procurement}

@@

\section{Methods and experimental design}
\label{sec:methods}
\input{sections/methods.tex}

@@

This project is also developed as open-source. \url{https://github.com/PyPSA/247-cfe}

@@

\section*{Supplementary Information}
\label{sec:si}

\section{Technology assumptions}
\label{sec:si_1}
\input{sections/supplementary_1.tex}

\section{Background system assumptions}
\label{sec:si_2}
\input{sections/supplementary_2.tex}

\section{Mathematical formulation of clean energy procurement}
\label{sec:si_3}
\input{sections/supplementary_3.tex}

% \addcontentsline{toc}{section}{Supplementary References}
% \renewcommand{\ttdefault}{\sfdefault}
% \bibliographyS{paper_247CFE}

### 2023-10-10 manuscript/sections/introduction.tex
manuscript: coordinate all chapters, complete methods

Climate change is driving a global effort to rapidly decarbonise electricity systems across the globe. 
The European Union (\gls{eu}) has committed to achieve net-zero emissions by 2050, and the European Commission has adopted the European Climate Law with a target of reducing net greenhouse gas emissions by at least 55\% by 2030, compared to 1990 levels \cite{EuropeanClimateLaw2020}. 
National climate initiatives span the globe, including the United States with the Biden administration's goal of reducing emissions by 50-52\% by 2030, compared to 2005 levels \cite{BidenClimatePlan2021}, and China's commitment to \enquote{have \co emissions peak before 2030 and achieve carbon neutrality before 2060} \cite{ChinaNetZero-IEA}.

@@

The remainder of the paper is structured as follows: Section \cref{sec:methods} gives a brief summary of methodology, sources of model input data, and the experimental setup. The results are presented and discussed in Section \cref{sec:results} and put in perspective in Section \cref{sec:discussion}. The work is concluded in Section \cref{sec:conclusion}.

>>>>

Climate change is driving a global effort to rapidly decarbonise electricity systems across the globe. 
The European Union (\gls{eu}) has committed to achieve net-zero emissions by 2050, and the European Commission has adopted the European Climate Law with a target of reducing net greenhouse gas emissions by at least 55\% by 2030, compared to 1990 levels \cite{EuropeanClimateLaw2020}. 
National climate initiatives span the globe, including the United States with the Biden administration's goal of reducing emissions by 50-52\% by 2030, compared to 2005 levels \cite{BidenClimatePlan2021}, and China's commitment to have \co emissions peak before 2030 and achieve carbon neutrality before 2060 \cite{ChinaNetZero-IEA}.

@@

The remainder of the paper is structured as follows: \cref{sec:methods} gives a brief summary of methodology, sources of model input data, and the experimental setup. 
The results are presented and discussed in \cref{sec:results} and put in perspective in \cref{sec:discussion}. 
The work is concluded in \cref{sec:conclusion}. 
\nameref{sec:si} provides further details about model assumptions, background energy system parametrisation, and the clean energy procurement mathematical model.

### 2023-10-10 manuscript/sections/methods.tex
manuscript: coordinate all chapters, complete methods

\textbf{Clean energy procurement --} We introduce new model components (parameters, variables, constraints) to model voluntary clean energy procurement.
By incorporating these into the mathematical problem, we model a situation when a fraction of electricity demand in a particular bidding zone is committed to procuring additional clean energy with a desired strategy.
The fraction is set at 10\% of the total \gls{ci} electricity demand in a particular bidding zone, unless otherwise stated (hereinafter referred to as \enquote{participating consumers}).
Accordingly, the model co-optimises the procurement and operational decisions of the participating consumers to meet their electricity demand in accordance with the procurement strategy they have chosen.
The mathematical formulation of the clean energy procurement model is provided in the \nameref{sec:si}.

@@

\textbf{Technology assumptions --}

Cost and other assumptions for energy technologies available for participating consumers were taken primarily from the Danish Energy Agency \cite{DEA-technologydata} for the respective years and are provided in Table S1. 
For a full list of technology assumptions, see the GitHub repository [TODO]. 
For the \gls{ldes}, we assume an underground hydrogen storage in salt caverns with an electolyzer and a fuel cell for hydrogen conversion. 
Data for advanced clean firm technologies is less reliable due to technological uncertainty and lack of commercial experience. 
We use the cost assumptions from the available literature and own indicative assumptions (see Table S1).

\textbf{Other assumptions --}

In all the modelled countries, renewable generation must meet the political targets as defined in the NECPs or by more recent national policy targets (such as the Easter
package in Germany), see Table 1.

>>>>

\textbf{Clean energy procurement --} We introduce new model components (parameters, variables, constraints) to model voluntary clean energy procurement.
By incorporating these into the mathematical problem, we model a situation when a fraction of electricity demand in a particular bidding zone is committed to procuring additional clean energy with a desired strategy.
The fraction is set at 10\% of the total \gls{ci} electricity demand in a particular bidding zone, unless otherwise stated (hereinafter referred to as \enquote{participating consumers}).
Accordingly, the model co-optimises the procurement and operational decisions of the participating consumers to meet their electricity demand in accordance with the procurement strategy they have chosen.
The mathematical formulation of the clean energy procurement model is provided in supplementary material [\labelcref{sec:si_3}].

@@

\textbf{Technology assumptions --} Cost and other assumptions for energy technologies available for participating consumers were collected primarily from the Danish Energy Agency \cite{DEA-technologydata} for the respective years and are provided in Table S1. 
For the \gls{ldes}, we assume an underground hydrogen storage in salt caverns with an electolyzer and a fuel cell for hydrogen conversion. 
Data for advanced clean firm technologies is less reliable due to technological uncertainty and lack of commercial experience. 
We use the cost estimates from the available literature and own indicative assumptions (see Table S1).

\textbf{Other assumptions --} Other model inputs and key background system assumptions are provided in [\labelcref{sec:si_2}]. For a full list of technology assumptions, see the GitHub repository \cite{github-247CFEpaper}.

### 2023-10-10 manuscript/sections/results.tex
manuscript: coordinate all chapters, complete methods

% TODO refine and shorten the results section
% Maybe move some of the graphs to the annex
% and all other graphs to a dashboard

Throughout the analysis, we examine how voluntary clean electricity procurement strategies affect both buyers and the electricity system as a whole.
From the \gls{ci} buyers' perspective, we examine optimal procurement strategies (i.e., a mix of locally procured energy generation and storage assets and electricity imports), the average cost of procured electricity and the carbon emissions associated with electricity usage (also known as Scope 2 emissions).
From a system perspective, we analyze how voluntary clean energy procurement impacts \co emissions in the region and the \enquote{demand pull} for advanced energy technologies.

@@

We explored the means, costs, and impacts of clean electricity procurement in the European electricity system for the year 2025 in the sections above.
In this section, we examine the results and implications of these procurement strategies for 2030.
Ultimately, this will allow us to better understand the long-term effects and the potential evolution of clean energy procurement in Europe, as companies continue to adapt their procurement strategies.

A five-year step to 2030 changes many system parameters from a modelling perspective.
In partcular, technology costs decline as a result of economies of scale and incremental innovation, energy- and climate policies become tighter, and some legacy power plants go out of business.
The two key trends of advancing five years forward are cleaner electricity grids and lower costs for energy technologies.

@@

\begin{figure}[H]
    \centering

>>>>

Throughout the analysis, we examine how voluntary clean electricity procurement strategies affect both buyers and the electricity system as a whole.
From the \gls{ci} buyers' perspective, we examine optimal procurement strategies (i.e., a mix of locally procured energy generation and storage assets and electricity imports), the average cost of procured electricity and the carbon emissions associated with electricity usage, also known as Scope 2 emissions \cite{GHGProtocolScope2}.
From a system perspective, we analyze how voluntary clean energy procurement impacts \co emissions in the region and the \enquote{demand pull} for advanced energy technologies.

@@

We explored the means, costs, and impacts of clean electricity procurement in the European electricity system for the year 2025 in the sections above.
In this section, we examine the results and implications of these procurement strategies for 2030.
To recall the \nameref{sec:methods} section, the key trends of advancing five years forward are cleaner electricity grids and lower costs for energy technologies.

@@

\begin{figure}
    \centering
